Scenario 2 - MPX in the EU

### 2022-11-21 MS4.Rmd
Table with gender and age

```{r packages, include=FALSE}
library(ggplot2)
library(tidyverse)
library(readr)
library(lubridate)
library(stringr)
library(readxl)
library(kableExtra)
```

@@

>>>>

```{r packages, include=FALSE}
library(ggplot2)
library(tidyverse)
library(readr)
library(lubridate)
library(stringr)
library(readxl)
library(kableExtra)
library(janitor)
library(DT)
```

@@

```{r}
euro_census_stats2 <- read_csv("files/euro_census_stats.csv")
euro_census_stats2 <- euro_census_stats2 %>%
  mutate(AGE = case_when(AGE %in% c("Y_LT15") ~ "Age < 15",
                                  AGE %in% c("Y15-29") ~ "Age 15-29",
                                  AGE %in% c("Y30-49") ~ "Age 30-49",
                                  AGE %in% c("Y50-64") ~ "Age 50-64",
                                  AGE %in% c("Y65-84") ~ "Age 65-84",
                                  AGE %in% c("Y_GE85") ~ "Age 85 and Older")) %>%
  filter(pop > 0) %>%
  select(COUNTRY_CODE, SEX, AGE, pop) %>%
  ungroup() %>%
  group_by(COUNTRY_CODE, SEX, AGE) %>%
  summarise("age_category_count" = sum(pop)) %>%
  ungroup() %>%
  group_by(COUNTRY_CODE) %>%
  mutate(total_pop = sum(age_category_count)) %>% ungroup()

euro_mpx_cases2 <- read_csv("files/euro_mpx_cases.csv")
euro_mpx_cases2 <- euro_mpx_cases2 %>%
  rename(COUNTRY_CODE = CountryCode) %>%
  group_by(COUNTRY_CODE) %>% 
  summarize(total_cases = sum(ConfCases))

demo_data <- left_join(euro_census_stats2, euro_mpx_cases2, by = "COUNTRY_CODE") %>%
  drop_na(total_cases) %>%
   mutate(COUNTRY_CODE = case_when(COUNTRY_CODE %in% c("AT") ~ "Austria",
                                   COUNTRY_CODE %in% c("BE") ~ "Belgium",
                                   COUNTRY_CODE %in% c("BG") ~ "Bulgaria",
                                   COUNTRY_CODE %in% c("HR") ~ "Croatia",
                                   COUNTRY_CODE %in% c("CY") ~ "Cyprus",
                                   COUNTRY_CODE %in% c("CZ") ~ "Czechia",
                                   COUNTRY_CODE %in% c("EE") ~ "Estonia",
                                   COUNTRY_CODE %in% c("FI") ~ "Finland",
                                   COUNTRY_CODE %in% c("FR") ~ "France",
                                   COUNTRY_CODE %in% c("EL") ~ "Greece",
                                   COUNTRY_CODE %in% c("HU") ~ "Hungary",
                                   COUNTRY_CODE %in% c("IE") ~ "Ireland",
                                   COUNTRY_CODE %in% c("LV") ~ "Latvia",
                                   COUNTRY_CODE %in% c("LU") ~ "Luxembourg",
                                   COUNTRY_CODE %in% c("MT") ~ "Malta",
                                   COUNTRY_CODE %in% c("PL") ~ "Poland",
                                   COUNTRY_CODE %in% c("PT") ~ "Portugal",
                                   COUNTRY_CODE %in% c("RO") ~ "Romania",
                                   COUNTRY_CODE %in% c("SK") ~ "Slovakia",
                                   COUNTRY_CODE %in% c("SI") ~ "Slovenia")) %>%
  group_by(COUNTRY_CODE, SEX, AGE, total_cases, total_pop) %>%
  mutate('age_cat_pct' = round((age_category_count/total_pop*100),digits = 2)) %>%
  select(COUNTRY_CODE, SEX, AGE, total_cases, total_pop, age_cat_pct) %>%
  pivot_wider(names_from = AGE, values_from = age_cat_pct) %>%
  group_by(COUNTRY_CODE, SEX) %>%
  select(-c(total_pop)) %>%
  arrange(desc(total_cases))

kable(demo_data, "latex", booktabs = T,
      col.names = c("Country",
                    "Sex",
                    "MPX Cases",
                    "Age < 15 (%)",
                    "Age 15-29 (%)",
                    "Age 30-49 (%)",
                    "Age 50-64 (%)",
                    "Age 65-84 (%)",
                    "Age 85 and Older (%)"),
      caption = "European Countries by Sex and Age Category") %>%
  kable_styling(latex_options = "HOLD_position")
